Time Series Analysis of Chaotic Dynamical Systems with Recurrent Neural Networks

### 2019-04-23 doc/paper/paper.tex
Updates from Overleaf

\begin{equation}
   F_g^{(i)} = m_i \frac{\mathrm{d}^2 \rv_i}{\mathrm{dt}^2} =
   \sum_{j \neq i} G \frac{m_i m_j \hat{\rv}_{ij}}{\norm{\rv_{ij}}^3}
   \label{eq:nbody}
\end{equation}

@@

For example, given some neural network model $\yv(\xv; \wv)$, where $\xv$ is
known input data, $\wv$ is the model's parameters, and $\yv$ approximates
some values, $\tv$, then we define an objective function as the sum of
squared error:

@@

\begin{equation}
    \Ev(\xv; \wv) = \vert \vert \yv(\xv; \wv) - \tv \vert \vert_2^2.
    \label{eq:error_eq_rnn}
\end{equation}

@@

Third, the training values are fed into the model to sample the network with 
teacher-forced output. We define a matrix $M$ to store the input unit values,
bias, and internal state value pairs, $(\uv(t_{T_0}), 1, \xv(t_{T_0})), \dots,
(\uv(t_T), 1, \xv(t_T))$, in its rows. We define a matrix $T$ to store the 
output unit values: $\dv(t_{T_0}), \dots, \dv(t_T)$.

>>>>

\begin{equation}
   F_g^{(i)} = m_i \frac{\mathrm{d}^2 \rv_i}{\mathrm{dt}^2} =
   \sum_{j \neq i} G \frac{m_i m_j \rv_{ij}}{\norm{\rv_{ij}}^3}
   \label{eq:nbody}
\end{equation}

@@

For example, given some neural network model $\yv(\xv; \wv)$, where $\xv$ is
known input data, $\wv$ is the model's parameters, and $\yv$ approximates
some values, $\dv$, then we define an objective function as the sum of
squared error:

@@

\begin{equation}
    \Ev(\xv; \wv) = \vert \vert \yv(\xv; \wv) - \dv \vert \vert_2^2.
    \label{eq:error_eq_rnn}
\end{equation}

@@

Third, the training values are fed into the model to sample the network with 
teacher-forced output. We define a matrix
$M \in \mathbb{R}^{(K + 1 + N) \times (T-T_0+1)}$
to store the input unit values,
bias, and internal state value pairs, $(\uv(t_{T_0}), 1, \xv(t_{T_0})), \dots,
(\uv(t_T), 1, \xv(t_T))$, in its columns. We define a matrix
$T \in \mathbb{R}^{L \times (T-T_0+1)}$ to store the 
output unit values: $\dv(t_{T_0}), \dots, \dv(t_T)$.
